Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
Restate a hint to the web frontend
... Since at this point it has already been introduced.

% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation

@@

% TODO: Decide on analysis tools
% * Weka
% * Some Boxplots including averages for all metrics
% TODO: Introduce the analysis tools we used

@@

This kind of analysis may be helpful for individual developers who seek to improve their Git etiquette. Because of this, we developed a web-frontend to our commit rater with integrated analysis. The source-code can be found on GitHub: \url{https://github.com/hartenfels/Commit-Rater-Web}

\TODO{Insert Screenshot of Commit Rater Web, maybe describe a little bit more}

>>>>

@@

@@

This kind of analysis may be helpful for individual developers who seek to improve their Git etiquette. Our aforementioned Web-Frontend exposes this kind of functionality in an easily accessible way.
